\subsection*{\color{draculapurple}About Me}
I am currently looking for work in the Software Engineering field. I'm employed by Lockheed Martin Canada (LMC) as a Software Engineer. While in LMC I worked on the Halifax Class Modernization Project and my primary tasks were related to the Combat Management System 330 (CMS 330). My primary responsibilities at LMC were: investigating problems reported by end users and testers; designing and implementing solutions to problems and new features; writing reports and presentations of investigation results, change proposals, summery of work done on the project including idiosyncrasies. I learned how to work with a complex system with many subsystems with their own unique functions. I have substituted as team lead when our scrum master when our team lead was away.

I have developed on both Windows and Linux platform using various IDE's including Visual Studio, Eclipse and Emacs. I used svn at my work and I use git for personal projects. I know how to set up virtual environment with Oracle VirtualBox and PodMan Containers. My programming experience is with Java 11, C/C++ and Python.
% I have created various data structures with C++ and used C++ to program on Robot Operating System.
I used Python with NumPy and MatPlotLib with analyze data captured from oscilloscopes and various other sensors including ultrasonic and LiDAR. I have written PowerShell script and bash script and am comfortable working in a command line environment.

I have learned black box testing while working at Blackberry Ltd and Synaptive Medical. There I did scripted and exploratory testing to evaluate the stability of their products, and filing bug reports on JIRA. I have created benchmarks to do performance testing. I have learned Agile development practices.

I have good writing skills. I use \LaTeX, Microsoft Office and other office software (LibreOffice/OpenOffice) to create reports and presentations. I have the ability to conduct research (from journals and other scholarly publications) and write academic / research papers.
