\documentclass[12pt]{article}
\pdfminorversion=7
\renewcommand*\familydefault{\sfdefault}
\renewcommand{\thepage}{}
\usepackage[
  pdftitle={NAFISA MASRUR COVER LETTER},
  pdfauthor={NAFISA MASRUR},
  pdfsubject={COVER LETTER},
  unicode,
  colorlinks=true
]{hyperref}

\usepackage[letterpaper, margin=1in]{geometry}

\begin{document}
\begin{center}
  \textbf{\huge NAFISA MASRUR}

  Halifax, NS $|$ 902-809-0937 $|$ \href{mailto:nafisa.mkhann@gmail.com}{nafisa.mkhann@gmail.com}\hrule
\end{center}

\setlength{\parindent}{0mm}
Becca Miller \\
Recruitment Manager \\
Bayers Lake Community Outpatient Centre \\
420 Susie Lake Crescent, Beechville, NS B3S 0G4

\vspace{1em}
\today
\vspace{1em}

\textbf{Re: Medical Lab Assistant in Training and Ref \#147412}
\vspace{1em}

Dear Ms. Becca Miller,
\vspace{1em}
\setlength{\parindent}{1em}

I am writing to express my interest in the \textbf{Medical Laboratory Assistant in Training}  position at Bayers Lake Community Outpatient Centre, as advertised. With a strong background in laboratory procedures, hands-on clinical experience, and a bachelor's degree in chemical engineering, I bring a unique combination of technical skills, accuracy, and patient-centered care.

\vspace{1em}

During my practicum at Cobequid Community Health Centre, I developed key skills that align directly with this role:
\begin{itemize}
\item Collected, labeled, and prepared specimens (blood, urine, swabs) following NSH SOPs, WHMIS, and infection control standards.
\item Assisted in patient registration, requisition verification, and documentation using Meditech and other databases.
\item Maintained a clean, organized phlebotomy area while ensuring compassionate patient interaction and comfort.
\item Collaborated with laboratory technologists and nursing staff to support urgent testing needs and patient flow, while providing compassionate patient care.
\end{itemize}

I am excited by the opportunity to contribute to Bayers Lake Community Outpatient Centre's commitment to patient-centered care and diagnostic excellence. My strong technical background, combined with a proven ability to balance laboratory accuracy with patient interaction, will allow me to contribute to both timely results and positive patient experiences. I welcome the chance to further discuss how my skills can support your team's success.

\setlength{\parindent}{0mm}\vspace{1em}

Sincerely,

\vspace{3em}

Nafisa Masrur

\end{document}
