\documentclass[11pt]{article} % twocolumn
\pdfminorversion=7
%% \RequirePackage{xcolor}

\renewcommand*\familydefault{\sfdefault}
\renewcommand{\thepage}{}
\renewcommand{\thesection}{}

\setlength{\parindent}{0mm}

\usepackage[legalpaper, margin=10mm]{geometry}

\usepackage[
  pdftitle={NAFISA MASRUR CV},
  pdfauthor={NAFISA MASRUR},
  pdfsubject={CV},
  unicode,
  colorlinks=true
]{hyperref}
%% \usepackage{multicol}

\newcommand{\cvsection}[1] {
  \begin{center}
    \large\textbf{#1}
  \end{center}
}

\begin{document}

\begin{center}
  \textbf{\huge NAFISA MASRUR}

  Halifax, NS $|$ 902-809-0937 $|$ \href{mailto:nafisa.mkhann@gmail.com}{nafisa.mkhann@gmail.com}\hrule
\end{center}

\cvsection{Professional Summary}
Competent and detail-oriented Medical Laboratory Assistant in training, graduated from CBBC Career College. Holds a bachelor's degree in chemical engineering with hands-on laboratory experience. Skilled in specimen handling, data management and administrative procedures. Strong foundation in scientific principles and lab safety. Proven administrative background and office coordination, bringing exceptional organizational and communication skills to support healthcare teams.

\cvsection{Education}

\paragraph{Medical Laboratory Assistant Program} \emph{CBBC Career College, Dartmouth} \hfill Nov 2025

\paragraph{Bachelor of Science in Chemical Engineering} \emph{Qatar University, Qatar} \hfill May 2019

\cvsection{Relevant Experiences}

\paragraph{Cobequid Community Health Centre} \emph{Lower Sackville, NS} \hfill Sept 2025 -- Nov 2025

\paragraph{Victoria General Hospital} \emph{Halifax, NS}

\paragraph{Bayers Lake Community Outpatient Centre} \emph{Halifax, NS}
%textbf

Completed 200 hours of hands-on practicum in a clinical setting.

\begin{itemize}
  \setlength\itemsep{-1mm}
\item Collected and labeled various specimens including blood, urine and swabs following proper safety and hygiene protocols.

\item Prepared specimens for transportation and laboratory analysis following Nova Scotia Health Standard Operating Procedures, WHMIS guidelines and infection control standards.

\item Assisted in patient registration, requisition verification and maintained accurate documentation.

\item Utilized \textbf{Qmatic} and other medical databases to update patient information and track specimen status.

\item Maintained a clean and organized phlebotomy area, ensuring equipment and supplies were stocked and sterilized.

\item Interacted with patients compassionately while ensuring procedural understanding and comfort.

\item Collaborated with lab technologists and nursing staff to support clinic flow and urgent testing needs.
\end{itemize}

\cvsection{Lab Experience}
\textbf{Chemistry Lab Assistant} \hfill Jan 2018 -- Jan 2019\\
\emph{Qatar University}
\begin{itemize}
  \setlength\itemsep{-1mm}
\item Performed pipetting, titration, spectrometry and chromatographic techniques.
\item Prepared and handled chemical reagents.
\item Maintained and calibrated lab equipment.
\item Followed strict health, safety and contamination control protocols.
\item Documented findings and lab results with accuracy and precision.
\end{itemize}

%% \newpage

\cvsection{Administrative Experience}
\textbf{Administrative Assistant} \hfill Jan 2022 -- Jan 2023 \\
\emph{Prime Veritas General Trading \& Contracting Co. W.L.L, Doha}
\begin{itemize}
  \setlength\itemsep{-1mm}
\item Managed executive scheduling and coordinated internal/external meetings.
\item Prepared HR statistical reports, memos and correspondence.
\item Maintained digital records and supported recruitment processes.
\end{itemize}

\textbf{HR Administrative Assistant} \hfill Jan 2020 -- Jan 2021 \\
\emph{Vision Development Project, Doha}
\begin{itemize}
  \setlength\itemsep{-1mm}
\item Supported HR operations including payroll, onboarding and training for about 200 personnel.
\item Maintained personnel files and drafted offer letters and HR documents.
\item Assisted with event and travel logistics for staff and executives.
\end{itemize}

\cvsection{Certifications \& Additional Training}
\begin{itemize}
  \setlength\itemsep{-1mm}
\item WHMIS (Workplace Hazardous Materials Information System)
\item First Aid \& CPR
\item Transportation of Dangerous Goods (TDG)
\item Occupational Health \& Safety (OH\&S)
\item Non-Violent Crisis Intervention
\end{itemize}

\cvsection{Languages}
\textbf{English} Fluent Reading, Fluent Writing, Fluent Speaking

\textbf{Bangla} Fluent Reading, Fluent Writing, Fluent Speaking

\textbf{Urdu} Intermediate Speaking
\end{document}
