\documentclass[12pt]{article} % twocolumn
\pdfminorversion=7
%% \RequirePackage{xcolor}

\renewcommand*\familydefault{\sfdefault}
\renewcommand{\thepage}{}
\renewcommand{\thesection}{}

\setlength{\parindent}{0mm}

\usepackage[a4paper, margin=10mm]{geometry}

\usepackage[
  pdftitle={TASNEEM ZAHUR CV},
  pdfauthor={TASNEEM ZAHUR},
  pdfsubject={CV},
  unicode,
  colorlinks=true
]{hyperref}

\newcommand{\cvsection}[1] {
  \begin{center}
    \large\textbf{#1}
  \end{center}
}

\begin{document}

\begin{center}
  \textbf{\huge TASNEEM ZAHUR}

  Doha, Qatar $|$ +974 5034-2622 $|$ \href{mailto:tasneemzahur@gmail.com}{tasneemzahur@gmail.com} $|$ \href{https://www.linkedin.com/in/tasneem-zahur/}{LinkedIn} \hrule
\end{center}

\cvsection{PROFESSIONAL SUMMARY}
Detail-oriented and motivated \textbf{Assistant Accountant} (\textbf{Accounts Receivable}) with a strong background in FMCG operations and financial reconciliation. Skilled in customer account management, statement preparation, and credit control functions. Proven ability to maintain accurate financial records, support sales operations, and strengthen customer relationships. Adept at working under pressure in fast-paced business environments.

\cvsection{CORE COMPETENCIES}
\begin{itemize}
  \setlength\itemsep{-1mm}

\item Accounts Receivable (AR) Management
\item Customer Account Reconciliation
\item Statement of Accounts (SOA) Preparation
\item Credit Control and Collections Follow-up
\item FMCG Sales Coordination Support
\item Financial Reporting and Documentation
\item ERP and Accounting Software (SAP / Oracle / Microsoft Dynamics)
\item Microsoft Office Suit of products
\end{itemize}

\cvsection{PROFESSIONAL EXPERIENCE}
\paragraph{Assistant Accountant - Accounts Receivable} \emph{ALI BIN ALI GROUP} \hfill Mar 2019 --- May2025

Key Responsibilities:
\begin{itemize}
  \setlength\itemsep{-1mm}
\item Managing the \textbf{Accounts Receivable (AR)} function for major FMCG clients.
\item Preparing and updating \textbf{default customer lists} for credit monitoring.
\item Sent Monthly \textbf{Statement of Accounts (SOA)} to top customers such as \textbf{Al Meera} and \textbf{Qatar Market Company}.
\item Conducting \textbf{customer account reconciliation} and resolved discrepancies or short payment promptly.
\item Providing \textbf{reconciled SOA reports} to customers on due date.
\item Monitoring outstanding balances and follow up with customers for timely payments.
\item Conducting the accounting task for maintenance of \textbf{Financial Credit notes and contracts}, also validate customer contracts.
\item Coordinating with the \textbf{sales team} by issuing system password for order processing.
\item Sending reminders and coordinate with \textbf{sales} or \textbf{Group Credit Control} teams for overdue accounts.
\item Performing \textbf{credit clearance} and monitoring customer credit limits and overdue status.
\item Assisting in monthly closing activities (GL analysis, Collection Projection and Collection Projection, Provision).
\item Ensuring compliance with company policies and internal audit requirements.
\end{itemize}

Achievements:
\begin{itemize}
  \setlength\itemsep{-1mm}

\item Reduced outstanding AR balances through timely follow-up and reconciliations.
\item Improved accuracy of customer SOA reports by streamlining reconciliation procedures.
\item Recognized by the finance team for maintaining high data accuracy and customer satisfaction.
\end{itemize}

\paragraph{Finance Department Internship} \emph{Qatar Steel} \hfill Jul 2017 --- Aug 2017
\begin{itemize}
  \setlength\itemsep{-1mm}
\item Acquired knowledge about Budgeting, Forecasting, Costing and how Qatar Steel updates their Actual Result and Forecasted Results.
\item Familiarization of Bank Reconciliation, Corporate Credit Cards and about the procedure of Corporate Credit Card and how many Departments of Qatar Steel use Corporate Credit Card.
%% \item Brief Introduction of Journal and General Ledger.
\item Familiarization of Financial Statements which include Statement of Financial Position, Statement of Comprehensive Income, Statement of changes in Equity and Statement of Cash flow.
%% \item Accomplished practical experience in Account Payable Process and Account Receivable Process of Qatar Steel.
%% \item Acquired general idea regarding Insurance Policies which are followed by Qatar Steel and what contents each Insurance policy includes.
%% \item Acquainted with various Reports prepared by Production units and other Departments and how they are compiled by the Finance Department to present it for Management's review.
\end{itemize}

\cvsection{EDUCATION}

\paragraph{Bachelor of Business Administration} \emph{Qatar University, Doha, Qatar} \hfill 2018

Major in Finance

\cvsection{TECHNICAL SKILLS}
\begin{itemize}
  \setlength\itemsep{-1mm}
\item ERP Systems: SAP, Oracle
\item MS Office Suite: Advanced Excel (VLOOKUP, Pivot Table, Reconciliation Templates)
\end{itemize}

\cvsection{LANGUAGES}
\textbf{English} Fluent Reading, Fluent Writing, Fluent Speaking

\textbf{Bangla} Fluent Reading, Fluent Writing, Fluent Speaking

\textbf{Urdu} Intermediate Speaking
\end{document}
